\documentclass[a4paper]{arthur-letter}

\title{I'm being unjustly smeared by Dianna Cowern, AKA Physics Girl, her family, and my immediate family Donald Burns, Anne Burns and Susan Burns}

\author{Matthew Woods, FKA Burns}

\usepackage[english]{babel}
\usepackage{fontspec}
\usepackage{luatexbase}
\usepackage{microtype}

% only needed for the example
\usepackage{lipsum}

%%=================%%
%%  Custom colors  %%
%%=================%%

% \definecolor{boxcolor}{HTML}{0E5484}
% \definecolor{maincolor}{HTML}{1a4c70}
% \definecolor{secondcolor}{HTML}{4d4d4d}

%%==========%%
%%  Header  %%
%%==========%%

% Set profile info [Following information are optional]
\letname{Matthew Woods}            % Your full name
\linkedin{matthew-woods-75bb721a5}       % Your linkedin
\mail{mattwoods243@gmail.com}       % Your email
\numberphone{408-613-3406}                % Your phone number
\lettitle{Alphabet Inc Lies, Blacklists and Conspiracy} % Title of your letter
\site{xignalx.com}                       % Your site
\github{https://github.com/XmattwoodsX}
\profilepic{}

\begin{document}
    \makeprofile % Set header
    
    % English commands (address and location at right and recipient at left)
    \address{Matthew Woods,\\PO Box 376\\Mountain View, CA, 94042}

    \begin{letter}

            \subject{TLDR: I'm a former Navy SEAL, smeared by Dianna Cowern (AKA Physics Girl) via Alphabet Inc while working as a Google employee. From 2015-2020, I have experienced severe police misconduct first hand. I think they may have ties to the Nazis, since my entire immediate family (Donald Burns, Anne Burns and Susan Burns) are Nazis... the type that agree with Adolf Hitler of WWII. They lied to me about this since I was born.}

            \opening{Dear New York Times,}

            For this story to make sense, I have to go back to the year 2013, when Dianna Cowern emailed me in response to a Craigslist ad that I placed for a male roommate. She replied, "What if it's a really cool girl?". I let her come see the house and she seemed fine, so I let her move in. We lived under the same roof for over two years, save a six month period where I provided anti-piracy contracting services to Maersk via The Trident Group as an APASS operator. We lived at two properties in San Diego, in the Soledad Mountain area of Pacific Beach, CA. Apparently the first house experience was so good she doubled down on having me live with her as a roommate. When I met her the first time, she casually mentioned that she was from Kauai, where I already had a future flight booked for vacation with my then girlfriend. She also mentioned that she had been living with a group of three SEALs prior to then... lot of coincidences. It is my belief that she was working with them and others (my family, the VA and other SEALs that I know from my service as a SEAL from 2001-2009) to defraud me and smear my name. Soon after moving in, she brought two of the SEALs to my house. They were so called "One Platoon Wonders": operators with exactly one combat deployment. They were active duty. They acted like they were her guard dogs, not SEALs. I know not of what they were thinking. However, they informed me of her cool "nickname" that they gave her: Dirty. I know a Dirty in the SEALs. I asked them if they knew him. They replied, in an aggressive, hissing tone with his real name. I don't have a clear motive, probably money. She mentioned once that she "thought about joining the CIA", which makes me suspicious of the CIA as well. I applied to the CIA in 2007 as a SEAL and never heard anything. I was granted TS/SCI in 2008 in order to attend advanced SEAL training, but I was never read in on any SCI programs. I never made contact with a CIA person, until Google in 2019 (an applicant to my data science team at Google). I did however try to apply as a General Response Staff (GRS) operator (SOC USA), only to find that they only accept operators who have an active clearance. Mine had expired, having been in school the previous four years. \\ 
            
            Inviting her in was a huge mistake. At this point (2013), I was separated from the Navy for four years, during which I earned my BS in Electrical Engineering and began applying to graduate school for the same. During my service as a SEAL, I saw combat in Iraq and the Philippines. Being a mediocre SEAL, I decided to leave and try something more in line with my then perceived strengths: math and scientific computing. I was living with friends at the time in a four bedroom house in Pacific Beach, CA (5328 Westknoll Dr). My "good friend" Garett McDermid offered me the room since he was moving for some reason. I think he was part of some setup, working with my then family, which I will get to later. I no longer associate with those people (Burns), opting to change my name to Woods, in honor of Ty Woods heroism in the 2012 Benghazi attacks. There are many characters in this story, but I will keep the focus on Dianna for the time being. After a month of living there, she introduced me to her SEAL buddies that she was supposedly living with before. They were new guys, just back from first deployment. They informed me that they nicknamed her "Dirty", the nickname of a famous SEAL that I was friends with at the time. I asked them, and they confirmed that they knew him. What is strange is that the original Dirty is quite evil and I never trust him. He is a war hero, though, in my eyes. He's most likely a psychopath. I think that was my first clue that something was off with this girl. If she is what I think she is, psychopath is a workable label. She may be a Nazi. My parents, on the other hand, are almost certainly Nazis, although I have not caught them doing anything illegal yet. I know this because they are my parents and have said many things over the years (e.g. Donald Burns: "I wonder if they will ever make a movie about WWII that is from the German side"). Dianna, I suspect by association, she never did anything to me overtly. Her parents may have been in contact with my parents and convinced her to do something. \\
            
            The main event with Dianna Cowern (AKA The Physics Girl) comes in 2015. She is a Youtube personality with over 1M subscribers. I lived with her for years. Something bad happened to me that year, probably some kind of Nazi attack. I became mentally unwell, fell in love with her and proposed all within a short period of time. I had no idea what she was... I thought friend and roommate of several years. I could not have been more wrong. She enacted a restraining order, which you can research with this link: \url{http://courtindex.sdcourt.ca.gov/CISPublic/casedetail?casenum=DV041758&casesite=SD&applcode=D}. I can read it today and laugh, but it bothered me for years that I couldn't explain what happened. Long story short, the contents of the restraining order contain factual information about what happened. It was put together by the physics students we were living with, including Dianna Cowern. It is extremely misleading. During that time, someone was anonymously calling the police on me almost every day in my home for "Wellness checks." I was being put in handcuffs a lot, but they never had any reason to arrest me. My Nazi roommates begged me to go to the VA for observation, since I was not behaving how they wanted me to behave. That is when I met Dr. Lehman of the VA La Jolla and a woman who never showed her face again (older, glasses, purple coat). Upon entry, she made care to say, "We don't ask about war crimes." It never sat right with me that she said that. "WTF is that supposed to mean?". Based purely on the testimony of these UCSD physics kids, the VA assigned me a diagnosis of Bipolar II, which I believe is false. I have struggled with depression for years, but that episode, at 32 years old, was the direct result of some kind of assault on me in plain view of the public. They are trying to create a narrative that I am mentally unwell in general, which is false. It is my goal to sue the VA and have everything they have written wiped from the electronic record. I went to the FBI in 2015 complaining of Nazis in the VA. They ignored me. \\
            
            I sit here in Oakland today in a tent. I have two defense trials coming on 24 Jun 2020 @ 0900: Hall of Justice, Dept 32, 200 W. Hedding St, San Jose, CA, 95110. I have evidence that my arraignment was compromised by the Sheriffs at the jail in support of the Nazi cause. They had me in the cell next to the court room in jail after three days of detention. I was told that I must sign something in order to not wear a mask. The sheriff asked me my jail ID number and name, then I signed. He did not like my signature, although it was the one I always use. He sent me back to jail for another three days because of that. Six days in, I finally get to trial. I sign my name declining the mask just as before. No problem this time. Then, after my public defender threw me under the bus by lying about me during the arraignment, I was in a cell right next to the court room. I grabbed a sheriff and said I have something to say to the judge (Ceras). They denied me the opportunity at the Sheriff level. I'm pretty sure they set me up with that specific public defender. I don't trust them anymore, so I will defend myself. The thing is, I experienced the San Jose police misbehaving for the first time in 2015: long before these incidents of the trials. During summer 2015, during the Dianna Cowern episode, I found myself with a layover in San Jose. I live in San Diego at that point. This is when the San Jose airport cops made their mistakes. They said too much to me. After tricking me into walking down an airport road (not a restricted area), I felt unwell and asked them to take me to a mental facility. An Iraqi airport cop put the cuffs on me excessively tight... I didn't understand why. I have never been attacked by a uniformed officer at this point. In the lobby of what they refer to as EPS, the Iraqi cop accused me of war crimes. "ENTIRE FAMILIES!!!" he claimed. I respond, "What proof is there of this?" He responds, "OH, THERE'S PROOF!!!" He didn't elaborate what proof he had, but I want to find out during this defense trial by getting him on the stand. I need money to do subpoenas of their notes. Fun fact, I used Dianna Cowern as my emergency contact in that scenario, thinking she would be on my side. Dead wrong. I will reiterate what I told him: I have never seen or participated in any kind of war crime. That is the truth. If an entire family was killed, I can think of only one unit that would be allowed to do that: The Naval Special Warfare Development Group (SEAL Team Six). I was on SEAL Team Five... AKA the "vanilla teams"... not SEAL team six. So, the officer's information is TS/SCI, or should have been. He was most likely working for Trump pre-election or some kind of ISIS sympathizer. I think they thought I would commit suicide because of all the stress. I did not. \\
            
            I found myself in the VA La Jolla mental unit many times in 2015, many times involuntarily. It was an attack. My ex father Donald Burns came out univited to San Diego and took up residence in my room without my permission. The roommates allowed that. He came to the VA La Jolla unannounced. His face was pure rage, like I was messing up his plans. He was drooling with rage. He barks, "What do you think about Trump!?" He is a Nazi, remember... my father. He hadn't shown his teeth to me like that since I was a boy. He was extremely abusive as a parent and stopped speaking with him mostly ever since. I allowed him to come to my graduations from events, that is about the extent in his involvement in my life, or so I thought. It turns out he has this whole thing planned with lies about me to everyone I know. The SEALs, UCSD, and now Silicon Valley at my employer... Google. \\
            
            I have reason to believe that Alphabet Inc, along with Youtube and Google, were working with the Cowerns (and my family) to discredit me and get me fired from Google. At Google, what I experienced and continue to experience, is them telling blatant lies about me around Silicon Valley, which is to say they are trying to blacklist me. I will mention that I have untraceable funds (\$10K) from Alphabet Inc, related to them trying to push me put of the company. They most likely have been manipulated by Physics Girl and my family to fire me. I don't think this is illegal, just highly damaging to Google and Youtube. During my tenure at Google, I saved a 100 Deloitte team from extreme failure single handedly. I did incredible work for them, sometimes not sleeping for days. They had a great year in business at Google Cloud thanks to me. My manager's comment after I delivered is, "This company would not have a business plan for 2019 if not for you." He also said, "I like your trajectory," more than once. I caught him in that lie when I told him I may stay for a few years, considering how successful I was there. He, Jorge Donoso, laughed a little at my comment. That was a clue that he was lying to me. Other events transpired there such that I quit unceremoniously one month before my "Googleversary"... unheard of. I did not trust them anymore, so I left. They never mentioned Dianna Cowern, but it could have been about her. OTH, my family was probably involved. They come up a lot. I'm going to subpoena every word ever written about be by Alphabet et al. I'm certain I will find some Physics Girl treachery. After Google, I was having problems with getting other jobs. They (Alphabet) give me bad references and tell lies about me to potential employers. It is undeserved, especially considering the sacrifices I made for them. They are lying about me:  why? \\
            
            The two cases for my defense are not simple. They involve the police continuing their trend of harassing me in the San Francisco Bay Area. San Jose is pretty bad, but Mountain View, Palo Alto and Santa Clara are right there with them. They are doing the same thing as the Iraqi airport cop... trying to set me up somehow. I suspect Trump, but no proof. I want to know if he knows who I am. If he does, news to me. I hate him and want to stop his fascist Nazi control over our country. Help me, NYT. I'm typing this on my iPhone. My thumbs are tired. I'm broke. Nothing is working for me. I'm alone. 

            \closing{Yours sincerely,} % To adapt following recipient

            \signing{Matthew Woods (FKA Burns)}

    \end{letter}

\end{document}
